### 2011-07-07 doc/theses/vitasek/diplomka.tex
Thesis: in progress

TODO talk about Fajt - but that's different, that's keys

@@

TODO mention things like Taboo search (we won't be using them)

>>>>

TODO talk about Fajt - but that's different, that's keys
TODO add citation for Fajt

@@

TODO mention things like Taboo search and Genetic Algorithms (we can emulate them with Crossover/Mutation) (we won't be using them)
